Joshua 2.0: An Open Source Toolkit for Machine Translation \\with Syntax, Semirings and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Changed title
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1606 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\title{2010 Progress Report to Joshua Toolkit : An Open Source Toolkit for Parsing-based Machine Translation\thanks{ 
Please cite Li et al. (2009a) if you use Joshua in your research, and not this paper.}}

@@

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit (written in Java) for parsing-based machine translation.
In the first version, it  has inimplemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
It has also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques have been exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

@@

\section{Supporting SAMT}
\todo{juri or ccb}

\section{Supporting Manual Constraints}
\todo{anni}

>>>>

\title{Joshua 2.0: An Open Source Toolkit for Machine Translation \\with Syntax, Semirings and Other Goodies }

@@

\textbf{Joshua} \cite{joshua-wmt09} is an open-source toolkit (written in Java) for parsing-based machine translation.
The first version implemented all the essential algorithms described 
in \newcite{hiero-2007}: chart-parsing, $n$-gram language model integration, beam- and cube-pruning, and $k$-best extraction.  
The initial release also implemented suffix-array grammar extraction \cite{lopez:2007:EMNLP-CoNLL2007} 
and minimum error rate training \cite{och-mert}. 
Additionally, parallel and distributed computing techniques were exploited 
to make it scalable \cite{Joshua-old}. In the design of \joshua, we have applied general
principles of software engineering to achieve three
major goals: extensibility, end-to-end coherence,
and scalability.

@@

\section{Support for Syntax Augmented MT}
\todo{juri or ccb}

\section{Manual Constraints on the Input}
\todo{anni}
